---
title: "Welcome to R Workshop Series"
output: 
  html_document:
    theme: lumen
    highlight: tango
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Last updated 10/20/2017*

***

This site was set up to host the content taught during these sessions and are meant for students for reference or for self-study. It is split into different sessions: 

  * Installation and setup
  * Importing data 
  * Data cleansing 
  * Visualization 
  * Regression 
  
Stay tuned as we add additional sections!  

&nbsp; 

## Installation and setup

### Installation

What is R and why do we care?

Text-based
Transparent, reproducible, editable workflows
Lots of support online
What does a program do and what is a function and what does the logic do?

Good to show example and make interactive
show win/accomplishment
need problems & examples
maybe marry to Excel to show understanding data
Need to go through the environment (console vs editor), comments, and
Explanation of head()
Getting your window back
Go through the logic of packages/library
go through process of downloading new libraries
go through process of loading a library
When programs are done running (when console is done)
Parameters for new libraries, how do you know how many it takes?
Also, what does a data table mean in a parameter?
One dude wants to get into actually programming for consulting
Piping, go thru one step at a time
Office hours for actual practice application of these problems
Managing question flow for session
Airline problem might be way too many functions for students to handle, maybe focus on five or six and really drill down into
Rushing through these functions, need to really step through practice problems
Regression & Visualization should really be its own session
Explain that these sessions are meant for teaching code vs. working with professors to work out regression
ggplot library documentation
themed libraries
install packages ‘ggridges’
tidyverse library documentation
Session to show what libraries can do, but not necessarily meant to get you to expert level. Have to do practice problems
Regression
dummy variables + fixed effects?
O’Reilly & Visualization R e-book links
Links to good R teaching sites


## Example Problems

```{r}
library(nycflights13)

head(flights)
```


